Explore CNV distributions of reference cells: SCPCP000015

### 2025-05-28 analyses/infercnv-consensus-cell-type/exploratory-notebooks/02_ewings-reference-cnv.Rmd
some more text

@@

>>>>

This function prepares a TSV of `inferCNV` results by creating a `total_cnv_per_cell` column to summarize CNVs per cell.

@@

## Conclusions

It does not seem that reference cell CNV distributions are problematically overlapping with tumor CNV distributions now that references were updated to generate these re-processed results.
